Actuator line modeling of vertical-axis turbines

### 2018-05-05 paper.tex
Address reviewer 2 comments

The kinematics of a CFT are parameterized by the tip speed ratio $\lambda =
\omega R/U_\infty$, where $R$ is the maximum rotor radius, and $U_\infty$ is the
free stream velocity. In contrast to an AFT, which under ideal conditions can be
considered a steady machine, CFT blades encounter large amplitude and rapid
oscillations in angle of attack, often exceeding the rotor blades' static stall
angles in typical operation, which makes their blade loading and performance
more difficult to predict. The unsteadiness can be characterized by a reduced
frequency~\cite{Leishman2006}
\begin{equation}
    k = \frac{\omega c}{2 U_\infty},
\end{equation}
which assumes the free stream velocity is constant. Unsteady effects begin to
become significant for $k > 0.05$, and can become dominant for $k \ge 0.2$.

>>>>

The kinematics of a CFT are parameterized by the tip speed ratio $\lambda =
\omega R/U_\infty$, where $R$ is the maximum rotor radius, and $U_\infty$ is the
free stream velocity. In contrast to an AFT, which under ideal conditions can be
considered a steady machine, CFT blades encounter large amplitude and rapid
oscillations in angle of attack, often exceeding the rotor blades' static stall
angles in typical operation, which makes their blade loading and performance
more difficult to predict. The unsteadiness can be characterized by a reduced
frequency~\cite{Leishman2006}
\begin{equation}
    k = \frac{\omega c}{2 U_\infty},
\end{equation}
which assumes the free stream velocity is constant.
Unsteady effects begin to
become significant for $k > 0.05$, and can become dominant for $k \ge 0.2$.
Note $\omega$ in the reduced frequency equation refers to the frequency of
angle of attack oscillation, which is normally sinusoidal in pitching foil
experiments, but is analogous to cross-flow turbine blade kinematics, i.e.,
the angle of attack cycle encounted by a CFT blade has a period equal to one
turbine revolution.
